Influences of GDP in the U.S

### 2022-11-12 Manuscript/manuscript.tex
commit

\paragraph{Abstract}

\paragraph{Keywords}

\paragraph{Introduction}
%  the introduction sections need to explain the importance of the topic of the paper, provide the background of the research work, and highlight the contributions of the work. At the end of the introduction, a roadmap, or an outline of the paper is useful in helping the readers navigating through the following sections.
%Why does it matter?
%What have been done?
%What is new?

@@

Szustak found that the relationship between power production and GDP is random. This

Kalyoncu found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia."(cite dergipark thing). Their research focused on the relationship between energy consumption and economic growth.
The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply. 
% roadmap and contributions

@@

\paragraph{Data}
%Who collected the data (source)? How was the data collected? Sampling frame? Sampling approach? What period or range does the data cover?

@@

\paragraph{Methods} 
To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
Multiple linear regrssion is a continuation of simple linear regression. 
For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
The general form of the multiple linear regression model is as follows:

@@

\paragraph{Application}

@@

\paragraph{Discussion}

\paragraph{Appendix}

>>>>

\section*{Abstract}

\section*{Keywords}

\section*{Introduction}
%  the introduction sections need to explain the importance of the topic of the paper, provide the background of the research work, and highlight the contributions of the work. At the end of the introduction, a roadmap, or an outline of the paper is useful in helping the readers navigating through the following sections.
%Why does it matter?
%What have been done?
%What is new?

@@

\citet{szustak2021relationship} found that the relationship between power production and GDP is random. This

\citet{kalyoncu2013causality} found that there is "unidirectional causality from per capita GDP to per capita energy consumption for Armenia." Their research focused on the relationship between energy consumption and economic growth.
The countries they focused their study on, Georgia, Azerbaijan and Armenia from 1995 to 2009, all faced low energy supply.

@@

\section*{Data}
%Who collected the data (source)? How was the data collected? Sampling frame? Sampling approach? What period or range does the data cover?

@@

\section*{Methods}
To investigate which factors influence Gross Domestic Product, multiple linear regression will be used. 
Specifically, the variables Population, Business Sector Labor Productivity, 10 Year Treasury Constant Maturity Rate, Disposable Personal Income, Unemployment Rate, and Total Primary Energy Consumption will be used to predict United States Gross Domestic Product.
Multiple linear regrssion is a continuation of simple linear regression. 
For this model, there must be two or more independent predictors that are used to predict one dependent variable. 
The general form of the multiple linear regression model is as follows:

@@

\section*{Application}

@@

\section*{Discussion}
